### 2024-05-01 thesis/input_files/probabilistic.tex
melbourne kernels

>>>>

We conclude this chapter with reporting the same kind of tables \ref{tab:kernel pinball comparison}, \ref{tab:kernel pinball comparison quantile-wise}, \ref{tab:kernel mae comparison} and figures \ref{fig:kernel quantile regressors comparison} comparing various kernel functions.

% tables
\begin{table}[!h]
    \caption{Kernels comparison pinball loss Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Gauss RBF &  10.031708 \\
        & Laplacian &  10.056884 \\
        & Gauss RBFxLaplacian & 10.150826 \\
        & Cosine & 16.253973    \\
        & Linear & 10.463867    \\
        & Polynomial & 11.238393     \\
        & Sigmoid & 16.253973            \\
        & Chi squared & 10.023732       \\
        & Matern & \textbf{10.021369}  \\
        & Periodic  & 15.946272\\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

\begin{table}[!h]
    \caption{Kernels comparison pinball loss quantile-wise Melbourne data}
    \label{tab:kernel pinball comparison quantile-wise}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
    \toprule
    Kernel/Quantiles & 0.1 & 0.2 & 0.3 & 0.4 & 0.5 & 0.6 & 0.7 & 0.8 & 0.9 \\
    \midrule
    Gauss RBF &  \textbf{0.540145} &
    \textbf{0.903193} &
    1.173627 &
    1.368022 &
    1.456053 &
    1.447470 &
    \textbf{1.331375} &
    1.096649 &
    0.715013 \\
    Laplacian &  0.542499 &
    0.906517 &
    1.177309 &
    1.371198 &
    1.462111 &
    1.453119 &
    1.340193 &
    \textbf{1.095991} &
    0.707947 \\
    Gauss RBFxLaplacian &0.545787 &
    0.915559 &
    1.189965 &
    1.387109 &
    1.479901 &
    1.475541 &
    1.350803 &
    1.101151 &
    \textbf{0.704922} \\
    Cosine & 0.755479 &
    1.343973 &
    1.802603 &
    2.123425 &
    2.307123 &
    2.367123 &
    2.262603 &
    1.971644 &
    1.320411 \\
    Linear &  0.565663 &
    0.947889 &
    1.250009 &
    1.437863 &
    1.506723 &
    1.478379 &
    1.358865 &
    1.135702 &
    0.782660   \\
    Polynomial &   0.542573 &
    0.908681 &
    1.178357 &
    \textbf{1.362351} &
    1.450249 &
    1.455228 &
    1.339822 &
    1.107768 &
    0.744118  \\
    Sigmoid &   0.755479 &
    1.343973 &
    1.802603 &
    2.123425 &
    2.307123 &
    2.367123 &
    2.262603 &
    1.971644 &
    1.320411          \\
    Chi squared &   0.541430 &
    0.906352 &
    1.173164 &
    1.358862 &
    \textbf{1.444130} &
    \textbf{1.440915} &
    1.332140 &
    1.100262 &
    0.726625     \\
    Matern &  0.541192 &
    0.903209 &
    \textbf{1.169543} &
    1.364430 &
    1.451248 &
    1.442511 &
    1.332522 &
    1.096750 &
    0.716226 \\
    Periodic  & 0.759452 &
    1.352747 &
    1.809921 &
    2.125765 &
    2.314718 &
    2.379657 &
    2.274711 &
    1.976768 &
    1.328630 \\
    \bottomrule
    \end{tabular}
    \end{adjustbox}
\end{table}

\begin{table}[!h]
    \caption{Kernels comparison mean absolute error Melbourne data}
    \label{tab:kernel mae comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
         & Kernel & MAE \\
        \midrule
        & Gauss RBF &  3.024336 \\
        & Laplacian &  3.038633 \\
        & Gauss RBFxLaplacian &  3.070812\\
        & Cosine &    4.849589 \\
        & Linear &     3.142352\\
        & Polynomial &     3.064472 \\
        & Sigmoid &      4.849589       \\
        & Chi squared &    \textbf{3.022778}    \\
        & Matern &  3.024517 \\
        & Periodic  & 4.880673 \\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

% kernels figure

\begin{figure}[!h]
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_gaussian_rbf_kernel_quantile_regression.png} 
        \caption{Gauss RBF} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%% 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_laplacian_kernel_quantile_regression.png} 
        \caption{Laplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_gaussian_rbf_x_laplacian_kernel_quantile_regression.png} 
        \caption{Gauss RBFxLaplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%%
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_cosine_kernel_quantile_regression.png}
        \caption{Cosine} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_linear_kernel_quantile_regression.png}
        \caption{Linear} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_polynomial_kernel_quantile_regression.png}
        \caption{Polynomial} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \end{figure}

\begin{figure}[!h]\ContinuedFloat
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_sigmoid_kernel_quantile_regression.png}
        \caption{Sigmoid} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_chi_squared_kernel_quantile_regression.png}
        \caption{Chi squared} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_matern_kernel_quantile_regression.png}
        \caption{Matern} 
        \label{} 
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_periodic_kernel_quantile_regression.png}
        \caption{Periodic} 
        \label{} 
    \end{subfigure} 
    \caption{Kernel quantile regressors comparison}
    \label{fig:kernel quantile regressors comparison} 
\end{figure}
